---
title: "Introduction to catfda: Categorical Functional Data Analysis"
author: "Package Authors"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to catfda}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

```{r setup}
library(catfda)
```

## Introduction

The `catfda` package provides comprehensive tools for analyzing categorical functional data. It implements various methods for estimating latent Gaussian processes and probability curves from categorical time series data.

## Basic Usage

### Data Format

The package works with categorical functional data in two main formats:

1. **Categorical matrix (W)**: A matrix where rows represent time points and columns represent individuals, with categorical values (e.g., 1, 2, 3, "A", "B", "C")
2. **One-hot encoded array (X)**: A 3D array with dimensions (individuals × time × categories) containing binary indicators

### Simple Example

Let's start with a simple example using synthetic data:

```{r basic_example}
# Set parameters
set.seed(123)
n_time <- 50
n_individuals <- 10
time_points <- seq(0, 1, length.out = n_time)

# Generate synthetic categorical data (3 categories)
w_mat <- matrix(sample(1:3, n_time * n_individuals, replace = TRUE),
                nrow = n_time, ncol = n_individuals)

# Display the data structure
dim(w_mat)
head(w_mat)
```

### Estimation Methods

The package provides three main estimation approaches:

#### 1. Multinomial Approach

The multinomial method fits a single GAM with multinomial family:

```{r multinomial}
# Estimate using multinomial approach
result_multi <- estimate_categ_func_data("multinomial", time_points, w_mat)

# Check the output structure
names(result_multi)

# Dimensions of latent processes (Z) and probabilities (p)
dim(result_multi$z1_est)  # Latent process 1
dim(result_multi$p1_est)  # Probability for category 1
```

#### 2. Binomial Approach

The binomial method fits separate binomial GAMs for each category:

```{r binomial}
# Estimate using binomial approach
result_binom <- estimate_categ_func_data("binomial", time_points, w_mat)

# The output structure is similar
names(result_binom)
```

#### 3. Probit Approach

The probit method uses adaptive switching between probit and binomial links:

```{r probit}
# Estimate using probit approach
result_probit <- estimate_categ_func_data("probit", time_points, w_mat)

# Same output structure
names(result_probit)
```

## Visualization

Let's visualize the estimated probability curves:

```{r visualization}
# Extract probability estimates for the first individual
p1_multi <- result_multi$p1_est[, 1]
p2_multi <- result_multi$p2_est[, 1]
p3_multi <- result_multi$p3_est[, 1]

# Create a plot
plot(time_points, p1_multi, type = "l", col = "red", lwd = 2, ylim = c(0, 1),
     xlab = "Time", ylab = "Probability",
     main = "Estimated Category Probabilities (Individual 1)")
lines(time_points, p2_multi, col = "blue", lwd = 2)
lines(time_points, p3_multi, col = "green", lwd = 2)
legend("topright", legend = c("Category 1", "Category 2", "Category 3"),
       col = c("red", "blue", "green"), lwd = 2)

# Add the observed categories as points
observed_cats <- w_mat[, 1]
points(time_points[observed_cats == 1], rep(0.05, sum(observed_cats == 1)),
       col = "red", pch = 16)
points(time_points[observed_cats == 2], rep(0.05, sum(observed_cats == 2)),
       col = "blue", pch = 16)
points(time_points[observed_cats == 3], rep(0.05, sum(observed_cats == 3)),
       col = "green", pch = 16)
```

## Working with Real Data

### Data Preprocessing

If your categorical data uses non-numeric labels, the package handles this automatically:

```{r preprocessing}
# Example with character labels
w_char <- matrix(sample(c("Low", "Medium", "High"), 30 * 5, replace = TRUE),
                 nrow = 30, ncol = 5)

time_points_short <- seq(0, 1, length.out = 30)

# The function automatically handles character labels
result_char <- estimate_categ_func_data("multinomial", time_points_short, w_char)

# Check how many categories were detected
length(grep("p[0-9]+_est", names(result_char)))
```

### One-hot Encoding

You can also work directly with one-hot encoded data:

```{r onehot}
# Convert categorical data to one-hot encoding
x_array <- get_x_from_w(w_mat)
dim(x_array)  # individuals × time × categories

# Use the one-hot data directly with probit method
result_direct <- estimate_categ_func_data_probit(time_points, x_array)
names(result_direct)
```

## Advanced Features

### Parallel Processing

For large datasets, use the parallel versions:

```{r parallel, eval=FALSE}
# Setup parallel backend (not run in vignette)
library(doParallel)
cl <- makeCluster(2)
registerDoParallel(cl)

# Use parallel estimation
result_parallel <- estimate_categ_func_data_probit_parallel(time_points, x_array)

# Don't forget to cleanup
stopCluster(cl)
```

### Custom Parameters

You can customize the estimation process:

```{r custom}
# Use more basis functions for smoother curves
result_smooth <- estimate_categ_func_data("multinomial", time_points, w_mat,
                                          n_basis = 35)

# Use different GAM method
result_reml <- estimate_categ_func_data("multinomial", time_points, w_mat,
                                        method = "REML")
```

## Simulation Studies

The package includes tools for generating synthetic data:

```{r simulation}
# Create smooth probability curves
n_time_sim <- 40
n_individuals_sim <- 8
time_sim <- seq(0, 1, length.out = n_time_sim)

# Generate probability curves with temporal patterns
p1 <- outer(sin(2 * pi * time_sim) * 0.2 + 0.4, rep(1, n_individuals_sim))
p2 <- outer(cos(2 * pi * time_sim) * 0.15 + 0.3, rep(1, n_individuals_sim))
p3 <- 1 - p1 - p2

# Ensure valid probabilities
p1 <- pmax(0.1, pmin(0.8, p1))
p2 <- pmax(0.1, pmin(0.8, p2))
p3 <- pmax(0.1, pmin(0.8, p3))
total <- p1 + p2 + p3
p1 <- p1 / total
p2 <- p2 / total
p3 <- p3 / total

prob_curves <- list(p1_est = p1, p2_est = p2, p3_est = p3)

# Generate synthetic categorical data
synthetic_data <- generate_categ_func_data(prob_curves)

# Analyze the synthetic data
result_synthetic <- estimate_categ_func_data("multinomial", time_sim,
                                             synthetic_data$w_mat)

# Compare true vs estimated probabilities for individual 1
plot(time_sim, p1[, 1], type = "l", col = "red", lwd = 3, ylim = c(0, 1),
     xlab = "Time", ylab = "Probability",
     main = "True vs Estimated Probabilities")
lines(time_sim, result_synthetic$p1_est[, 1], col = "red", lwd = 2, lty = 2)
lines(time_sim, p2[, 1], col = "blue", lwd = 3)
lines(time_sim, result_synthetic$p2_est[, 1], col = "blue", lwd = 2, lty = 2)
lines(time_sim, p3[, 1], col = "green", lwd = 3)
lines(time_sim, result_synthetic$p3_est[, 1], col = "green", lwd = 2, lty = 2)

legend("topright",
       legend = c("True P1", "Est P1", "True P2", "Est P2", "True P3", "Est P3"),
       col = rep(c("red", "blue", "green"), each = 2),
       lwd = 2, lty = rep(c(1, 2), 3))
```

## Conclusion

The `catfda` package provides flexible and efficient tools for categorical functional data analysis. The three estimation approaches (multinomial, binomial, probit) offer different trade-offs:

- **Multinomial**: Most statistically coherent, efficient for many categories
- **Binomial**: Flexible, allows different smoothing for each category
- **Probit**: Adaptive approach, good for rare events

Choose the method that best fits your data characteristics and research questions.

## References

For more details on the theoretical background and applications, see the package documentation and associated research papers.
